Operationally-Safe Peer-to-Peer Energy Trading in Distribution Grids: A Game-Theoretic Market-Clearing Mechanism

### 2022-01-14 papers/01 Reply round 1/response_TSG.tex

\textbf{Ms. Ref. No.: TSG-01404-2021}  \\
\textbf{Title: Operationally-Safe Peer-to-Peer Energy Trading in Distribution Grids: A Game-Theoretic Market-Clearing Mechanism}   \\
\textbf{Authors: G. Belgioioso, W. Ananduta, S. Grammatico, and C. Ocampo-Martinez}   \\
\textbf{Journal: IEEE Transactions on Smart Grid}

%\vspace{1cm}

\setcounter{page}{1}

% ADD HERE PREAMBLE TEXT
The authors would like to thank the Reviewers and the Associate Editor for their comments, which have helped us to improve the manuscript. We do hope that all the points raised have been addressed. {To help reviewing the revised manuscript,} the points have been divided up and marked AE, R1, R2, R3, and R4, for comments from Associate Editor, Reviewers 1, 2, 3, and 4, respectively. When appropriate, the corresponding marks can be found within the manuscript and the modifications according to the comments are highlighted in \textcolor{blue}{blue}. Furthermore, the cross references of equation labels, as mentioned by the reviewers and used in the answers, are adapted based on the revised manuscript. In addition, we also now include an appendix, where we show (i) the derivation and convergence of Algorithm 1 (the proof of Proposition 1) and (ii) An ad-hoc algorithm to project onto $\mc U_{N+1}$.%We have also removed some intermediate steps in the derivation of some (in)-equalities and displayed some equations in different forms to meet the page limit. These parts are highlighted in \textcolor{magenta}{magenta}.%Additionally, in order to adjust the contents into a technical note, we have streamlined some parts of the paper, which are highlighted in \textcolor{magenta}{magenta}.

@@

\query[R1-1]{This paper proposed a peer-to-peer energy market for prosumers as a generalized aggregative game. The paper is well written, and the research may be of value. The reviewer mainly concerns about the proposed algorithm.}
\ans{We thank the reviewer for the positive comment.}

\textit{The comments are as follows:}

\query[R1-2]{The feasibility of such scenarios still remains further discussions considering the capital costs of energy storage, interests conflicts of current electrical roles, and the engineering implementations involving such accurate models.}
\ans{We agree with the Reviewer. This work particularly shows how a distributed clearing mechanism that can be implemented in such scenarios as well as how peer-to-peer market scenarios in theory can be beneficial.}

\query[R1-3]{The charging and discharging efficiency are not considered in (5), which is sometimes acceptable, but requires explanations.  }
\ans{In the first version of the manuscript, we did not consider the charging and discharging efficiency as we assume the simplest model of the storage since modeling the components is not the main focus of this work. However, based on this reviewer comment, we now update the storage dynamics, which include the charging and discharging efficiencies. Therefore, for each storage unit, we consider two decision variables, i.e., the charging and discharging powers. The storage unit is now modeled as follows:}

{``\edit{The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics \cite{atzeni2013,zhong2019online}}}
%
\begin{equation}
%	\marginnote{\note{R1-3}\\ \note{R2-2}}
	\begin{aligned}
		\left.
		\begin{array}{c}
			\edit{	x_{i,h+1} =\eta_i^{\mathrm{st}} x_{i,h} +\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\frac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}),} \\[.2em]
			\underline{x}_i \leq x_{i,h+1} \leq \overline{x}_i, \\[.2em]
			\edit{	{p}_{i}^{\mathrm{ch}} \in [0,\overline{{p}}_{i}^{\mathrm{ch}}], \ \ {p}_{i}^{\mathrm{ds}} \in [0,\overline{{p}}_{i}^{\mathrm{ds}}],}
		\end{array}
		\hspace{-5pt} \right\} & \begin{matrix}
			\forall i \in \mc N^{\mathrm{st}}, \\ \forall h \in \mc H,
		\end{matrix} \\
		\edit{p_{i}^{\mathrm{ch}}= 0, \ \ p_{i}^{\mathrm{ds}}= 0,}\qquad \qquad & \forall i \notin \mc N^{\mathrm{st}},
	\end{aligned}
	\label{eq:x}
	\tag{5}
\end{equation}
{where $x_{i,h} $ denotes the state of charge (SoC) of the storage unit at time $h \in \mc H$%
%\footnote{In \cite{atzeni2013}, the charging and discharging power are defined separately, which is actually a better representation. However, the optimal strategies that they produce satisfies the constraint that charging and discharging must be mutually exclusive (see footnote 1 in \cite{atzeni2013}). From other papers, they usually have boolean variables to ensure this constraint and we want to avoid that.}
, \edit{$\eta_i^{\mathrm{st}}, \eta_i^{\mathrm{ch}}, \eta_i^{\mathrm{ds}} \in (0,1]$ denote  the leakage coefficient of the storage, charging, and discharging efficiencies, respectively, while }  %$b_i~=~-\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}$, with 
$T_{\mathrm{s}}$ and $e^{\mathrm{cap}}_{i}$ denote sampling time and maximum capacity of the storage, respectively. Moreover, $\underline{x}_i,\overline{x}_i  \in [0,1]$  denote the minimum and the maximum SoC of the storage unit of prosumer $i$, respectively, whereas $\edit{\overline p}^{\mathrm{ch}}_i \geq 0$ and $\edit{\overline p}^{\mathrm{ds}}_i \geq 0$ denote the maximum charging and discharging power of the storage unit. Finally, we denote by  $\mathcal{N}^{\mathrm{st}}\subseteq\mathcal{N}$ 	the set of prosumers that own a storage unit.''}

@@

We have also modified our game formulation and proposed algorithm in Section III to take into account this storage model update.

\query[R1-4]{The energy loss of the distribution network is also not considered.}
\ans{We do not include energy loss of the distribution network in the current setup and leave it for future work. In this manuscript, we focus on the game-theoretic formulation of the interaction among prosumers and the network operator and show that the problem can be solved efficiently. For an extension that includes energy losses, we may impose to each prosumer an additional linear cost function that depends on the losses caused by trading and use linear model of power line losses as in \cite[Section II]{moret2020}.}

\query[R1-5]{The individual variables, coupled relationships for these energy roles, and the corresponding dual variables should be explained specifically, along with the whole framework structure for equilibrium. The rationalities of the framework is not clear. At least, the current presentation is hard to follow.  }
\ans{
%\green{
In the revised paper, (i) we have provided a detailed description of each individual variable along with an explanation of its function in the algorithm; (ii) we have re-designed the main algorithm layout; and (iii) we have included a paragraph to present the targeted class of equilibria considered. Please, refer to the margin notes (R1-5) in Section III for the related changes and additions.
%}
}

\query[R1-6]{The P2P trading prices are given parameters, which are quite unreasonable. In fact, the P2P prices are the key variable in most literature.}
\ans{In this manuscript, we want to consider the most general problem formulation of peer-to-peer markets available in the literature. Following \cite{sorin2019,lecadre2020,baroche2019b}, a linear trading cost function is introduced in the problem formulation for the purpose of product differentiation or preference prices. %Furthermore, \cite{baroche2019} also adds a trading tariff or transaction cost encoded as a 1-norm cost function. 
	Furthermore, we may set $c_{\{i,j\}}^{\mathrm{tr}}=0$, and thus only consider the dual variable associated with the reciprocity constraints (Eq. {(8b)} in the revised manuscript) as the shadow price of bilateral trading \cite[Section 2.4]{lecadre2020}. Indeed the proposed algorithm can handle any case where $c_{\{i,j\}}^{\mathrm{tr}} \geq 0$, for all $\{i,j\} \in \mc E$.}

 \query[R1-7]{The algorithm requires too many iterations, which leads to poor feasibility in real applications, especially in distributed environment. }
 \ans{
%\green{
	The average computational time (obtained using a pc with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory) for the parallel updates of each prosumer (i.e., Algorithm 2) is $t_{\text{avg}}^{\text{pro}} = 74.5$ milliseconds; while for the DNO update (i.e., Algorithm 3), the average computational time is $t_{\text{avg}}^{\text{DNO}} = 1.13$  seconds. 
%
 Hence, the total running time of the proposed market-clearing algorithm (Algorithm 1) implemented on a distributed system can be approximatively calculated as
\begin{align*}
\text{total computation time} = \text{\# iterations for convergence } \times (t_{\text{avg}}^{\text{pro}} + 	t_{\text{avg}}^{\text{DNO}}),
\end{align*}
which yields running times of less than 23 minutes. 
%
We consider this computational-time requirement reasonable for day-head or also for intra-day scheduling purposes. Moreover, we note that the total running time can be considerably reduced by (i) using provably-convergent accelerated versions of our market-clearing mechanism, that can be easily devised by exploiting the algorithmic framework in \cite[\S~IV-B]{belgioioso2020semi} and in practice reduce (potentially, halve) the total number of iterations for convergence;
(ii) designing a more efficient ad-hoc algorithm to solve the projection step in Algorithm 3 (i.e., Algorithm 3 (i)); (iii) using a more computationally-powerful hardware to perform the DNO central updates, namely, Algorithm 3. Finally, we note that the main algorithm is scalable with respect to the prosumer population size, namely, the number of iterations for convergence is not affected by the total number of prosumers in the network (see Figure {10}). Moreover, the computation time of the local updates is virtually also independent from the prosumer population size, for constant connectivity levels of the trading network. Therefore, the previous approximation remains valid independently from the market size.
%} 
}

@@

\newpage
\section*{Answers to Reviewer 2}

\query[R2-1]{This manuscript proposes a game model for P2P energy trading in a distribution network considering network constraints and the DNO agent. The game model is a generalized game in which agents have coupled objectives and constraints. A distributed algorithm is developed to seek the equilibrium of the game. The topic of this manuscript is interesting, and the presentation is clear in general. The reviewer has some comments on the model and algorithm. }
\ans{We thank the Reviewer for the positive comment.}

\query[R2-2]{In common energy storage models, efficiency is usually a coefficient of the charging/discharging power. The storage model in (5) is uncommon as the authors take the efficiency $a_i$ as a coefficient of energy state $x_{ih}$. In related works (such as (6) in https://ieeexplore.ieee.org/document/8919970), the coefficient of energy states is usually called a leakage coefficient, describing energy leakage over time. References may be needed for (5), and please explain in what sense this storage model (5) is practical.  }
\ans{We thank the reviewer for raising this point and suggesting the reference. In the first version of the manuscript, we did not consider the charging and discharging efficiency as we assumed the simplest model of the storage since component models are not the focus of this work. Nevertheless, based on this reviewer comment, we have updated the storage dynamics, which include the charging and discharging efficiencies. Therefore, for each storage unit, we consider two decision variables, i.e., the charging and discharging powers. The storage unit is now modeled as follows:}

{``\edit{The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics \cite{atzeni2013,zhong2019online}}}
%
\begin{equation}
	%	\marginnote{\note{R1-3}\\ \note{R2-2}}
	\begin{aligned}
		\left.
		\begin{array}{c}
			\edit{	x_{i,h+1} =\eta_i^{\mathrm{st}} x_{i,h} +\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\frac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}),} \\[.2em]
			\underline{x}_i \leq x_{i,h+1} \leq \overline{x}_i, \\[.2em]
			\edit{	{p}_{i}^{\mathrm{ch}} \in [0,\overline{{p}}_{i}^{\mathrm{ch}}], \ \ {p}_{i}^{\mathrm{ds}} \in [0,\overline{{p}}_{i}^{\mathrm{ds}}],}
		\end{array}
		\hspace{-5pt} \right\} & \begin{matrix}
			\forall i \in \mc N^{\mathrm{st}}, \\ \forall h \in \mc H,
		\end{matrix} \\
		\edit{p_{i}^{\mathrm{ch}}= 0, \ \ p_{i}^{\mathrm{ds}}= 0,}\qquad \qquad & \forall i \notin \mc N^{\mathrm{st}},
	\end{aligned}
	\label{eq:x}
	\tag{5}
\end{equation}
{where $x_{i,h} $ denotes the state of charge (SoC) of the storage unit at time $h \in \mc H$%
	%\footnote{In \cite{atzeni2013}, the charging and discharging power are defined separately, which is actually a better representation. However, the optimal strategies that they produce satisfies the constraint that charging and discharging must be mutually exclusive (see footnote 1 in \cite{atzeni2013}). From other papers, they usually have boolean variables to ensure this constraint and we want to avoid that.}
	, \edit{$\eta_i^{\mathrm{st}}, \eta_i^{\mathrm{ch}}, \eta_i^{\mathrm{ds}} \in (0,1]$ denote  the leakage coefficient of the storage, charging, and discharging efficiencies, respectively, while }  %$b_i~=~-\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}$, with 
	$T_{\mathrm{s}}$ and $e^{\mathrm{cap}}_{i}$ denote sampling time and maximum capacity of the storage, respectively. Moreover, $\underline{x}_i,\overline{x}_i  \in [0,1]$  denote the minimum and the maximum SoC of the storage unit of prosumer $i$, respectively, whereas $\edit{\overline p^{\mathrm{ch}}_i} \geq 0$ and $\edit{\overline p^{\mathrm{ds}}_i} \geq 0$ denote the maximum charging and discharging power of the storage unit. Finally, we denote by  $\mathcal{N}^{\mathrm{st}}\subseteq\mathcal{N}$ 	the set of prosumers that own a storage unit.''}

@@

We have also modified our game formulation and proposed algorithm in Section III to take into account this storage model update.

\query[R2-3]{In (9), the electricity price is defined to depend on the total consumption. This setting is often used in local energy systems (community or microgrid) but rarely used in wide-area energy networks (distribution networks). In real situations, the electricity prices in a power network are different at different buses and are determined by generation costs, power line congestion, power loss, etc. The reviewer understands that the authors deliberately use (9) to make the agents’ objectives coupled with each other. But the authors must explain why (9) is practical in the proposed model.  }
\ans{We agree with the Reviewer that the electricity price in (9) is more suitable for local energy systems than distribution networks as (9).   At the moment we consider the simplest model of electricity prices, which follows linear inverse demand function, i.e., the price increases when the demand does so. In other words, the cost function in (11) takes into account how congested the whole prosumer network is.   We note that the cost function defined by (9)--(11) already complicates the day-ahead problem compared to the existing P2P energy market literature. To our knowledge, most of the existing literature on P2P energy markets exclude the possible interaction between the prosumer network and the main grid, and do not have coupling cost function as in (11). In the revised manuscript, we acknowledge the inclusion of power line congestion and power loss in the formulation of electricity prices of the main grid as a potential future work. In addition, we may also generalize the grid cost function (9)--(11) by considering the total congestion per bus, i.e., the electricity price at each bus depends on the total demand of the prosumers connected to that particular bus.}

\query[R2-4]{In the proposed model, the DNO is considered a game player. This setting is also used in some other related works (such as https://ieeexplore.ieee.org/document/9223743). The authors may need a more comprehensive review on this aspect.  }
\ans{{We thank the reviewer for drawing our attention on this relevant paper that we cited and briefly reviewed in the new version of the introduction.}}

{\edit{``A similar approach is considered in \cite{zhong2020cooperative}, which employs generalized Nash bargaining theory and decomposes  a P2P market problem into two hierarchical subproblems (a social welfare maximization and an energy trading problem).''
}}

\query[R2-5]{The property of the game equilibrium is not clear enough. It is unclear what is the difference between v-GNE and GNE. The authors may need to formally (mathematically) define the variational GNE that the proposed game will reach. }
\ans{{We have included a more detailed explanation of the targeted class of variational generalized Nash equilibria, including a formal mathematical definition, as follows.}}

@@

\edit{``Among all GNEs, we target the special subclass of \textit{variational} GNEs (v-GNEs) that coincides with the solutions to a specific variational inequality GVI$(\mc K, P)$ \cite[Prop.~12.4]{facchinei201012},  i.e., the problem of finding a pair of vectors $(u^*,z^*)$, such that $u^* \in \mc K$, $z^* \in P(u^*)$, and
\begin{align*}
{(u - u^*)}^\top z^* \geq 0, \quad \forall u  \in  {\mc K}, 
\end{align*}
where the mapping $P(u^*): = \prod_{i \in \mc N^+} \frac{\partial}{\partial u_i} J_i(u_i^*,u_{-i}^*)$ is the so-called \textit{pseudo-subdifferential}, and $\mc K:= \mc C \cap (\prod_{i \in \mc N^+} \mc U_i)$ is the global feasible set.
%
v-GNEs enjoy the property of ``economic fairness”, namely, the marginal loss due to the presence of the coupling constraints is the same for each agent, see e.g. \cite{kulkarni2012variational}. For these reasons, v-GNEs have been used to model desirable (i.e., locally efficient, fair, and safe) configurations in several distributed engineering systems, including P2P energy market models, see e.g. \cite{lecadre2020}. In this paper, we focus on computational aspects, namely, the design and analysis of a fast and scalable decentralized v-GNE seeking algorithm for the P2P market game, while we study the properties of its v-GNEs numerically rather than analytically."
}

### 2022-01-14 papers/02 journal v2/journal_v14.tex
g
update manuscript and reply letter

%\paragraph*{highlight on considering physical constraints}
In practice, however, direct trading among prosumers might jeopardize system reliability, for which network operators are responsible. Therefore, when designing energy management mechanisms for a distribution grid, one must also consider the role of network operators and the reliability of the system itself.
%
For example, \cite{qin2018,morstyn2019} treat decentralized markets and operational reliability separately, and propose market-clearing mechanisms where decentralized market solutions must be approved by a network operator based on the system operational constraints. 
%
An alternative is based on incorporating network charges, which may reflect utilization fees and network congestion, into the market formulation, as discussed in \cite{baroche2019b,paudel2020}. Differently, \cite{moret2020,zhang2020} include network operators as players in the market and impose network operational requirements as constraints in the market problem, which is formulated as a multi-agent optimization. \marginnote{\note{R2-4}}\edit{A similar approach is considered in \cite{zhong2019online}, where an online decentralized control algorithm for distributed energy storage systems is developed. }

\paragraph*{Contribution} 
In this paper, we consider a P2P energy market in which each prosumer is capable of not only generating and storing energy but also directly trading with other prosumers as well as with the main grid. Similarly to \cite{moret2020}, we include a network operator, whose objective is to ensure safe and reliable operation  of the system. 
%
However, we formulate the market clearing as a GNE problem, in which the players (i.e., prosumers and network operators) have coupling objective functions and constraints (Section \ref{sub:setup}). \edit{Our market formulation extends our preliminary work \cite{belgioioso2020energy} by including network operational constraints and system operators in the model, which complicate the analysis as we need to exploit the problem structure to derive an efficient algorithm.}

@@

\smallskip
\subsubsection*{Notation}
$\R$ denotes the set of real numbers, $\bb N$ denotes the set of natural numbers, and  $\bs{0}$ ($\bs{1}$) denotes a matrix/vector with all elements equal to $0$ ($1$); to improve clarity, we may add the dimension of these matrices/vectors as subscript. $A \otimes B$ denotes the Kronecker product between the matrices $A$ and $B$. For a square matrix $A \in \R^{n \times n}$, its transpose is $A^\top$, $[A]_{i,j}$ represents the element on the row $i$ and column $j$. $A \succ 0$ ($\succcurlyeq 0$) stands for positive definite (semidefinite) matrix. Given $N$ vectors $x_1 \in \bb R^{n_1}, x_2 \in \bb R^{n_2},\ldots, x_N \in \R^{n_N}$, $x := \col\left(x_1,\ldots,x_N\right) = [ x_1^\top, \ldots , x_N^\top ]^\top$. \marginnote{\note{R4-9}}\edit{Given $x \in \bb R^n$, $\|x\|_A^2 = x^\top A x,$ with square matrix $A \succ 0$.}
%\smallskip
%\subsubsection*{Operator theoretic definitions}
%Here, $\Id(\cdot)$ denotes the identity operator. The mapping $\iota_{S}:\R^n \rightarrow \{ 0, \, \infty \}$ denotes the indicator function for the set $\mc{S} \subseteq \R^n$, i.e., $\iota_{S}(x) = 0$ if $x \in S$, $\infty$ otherwise. 
For a closed set $S \subseteq \R^n$, the mapping $\proj_{S}:\R^n \rightarrow S$ denotes the projection onto $S$, i.e., $\proj_{S}(x) = \argmin_{y \in S} \left\| y - x\right\|$. 
%The set-valued mapping $\nc_{S}: \R^n \rightrightarrows \R^n$ denotes the normal cone operator for the the set $S \subseteq \R^n$, i.e., $\nc_{S}(x) = \varnothing$ if $x \notin S$, $\left\{ v \in \R^n \mid \sup_{z \in S} \, v^\top (z-x) \leq 0  \right\}$ otherwise. 
%A set-valued mapping $\mathcal{F} : \R^n \rightrightarrows \R^n$ is (strictly) monotone if $(u-v)^\top  (x-y) \geq (>) \, 0$ for all $x \neq y \in \R^n$, $u \in \mathcal{F} (x)$, $v \in \mathcal{F} (y)$.
% $\fix\left( \mathcal{F}\right) := \left\{ x \in \R^n \mid x \in \mathcal{F}(x) \right\}$ and $\zer\left( \mathcal{F}\right) := \left\{ x \in \R^n \mid 0 \in \mathcal{A}(x) \right\}$ denote the set of fixed points and of zeros, respectively.

@@

\begin{figure}
	\centering
	%\includegraphics[scale=1.4]{figures/37bus_ex}
	\includegraphics[width=\columnwidth]{figures/NF/37bus_sysIPE1}
	\caption{Left plot: A modified IEEE 37-bus network with 12 prosumers (boxes) and 15 passive loads (black triangles); busses are represented by black circles, physical lines in $\mc L$ by solid lines. Right plot: P2P trading network, whereas trading relations ($\mc E$) are represented by blue double-arrow lines.
	}
	\label{fig:GGp}
\end{figure}

@@

\smallskip
\paragraph*{Storage units} 
Each prosumer might also minimize the usage of its storage units, for instance, in order to reduce its degradation. The corresponding cost function is denoted by $f_{i}^{\mathrm{st}}:\mathbb{R}^{H} \to \mathbb{R}$, defined as in \cite{hans2018}:
\begin{equation}
		%\marginnote{\note{R1-3}\\ \note{R2-2}}
f_{i}^{\mathrm{st}}(p_{i}^{\mathrm{ch}}, p_{i}^{\mathrm{ds}})= \|p_{i}^{\mathrm{ch}}\|_{Q_i^{\mathrm{st}}}^2 + \|p_{i}^{\mathrm{ds}}\|_{Q_i^{\mathrm{st}}}^2, \label{eq:f_st}
\end{equation}
where $Q_i^{\mathrm{st}}\succcurlyeq0$. \edit{The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics}
%
\begin{equation}
	\marginnote{\note{R1-3}\\ \note{R2-2}}
	\begin{aligned}
		\left.
		\begin{array}{c}
		\edit{	x_{i,h+1} =\eta_i^{\mathrm{st}} x_{i,h} +\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\frac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}),} \\[.2em]
			\underline{x}_i \leq x_{i,h+1} \leq \overline{x}_i, \\[.2em]
		\edit{	{p}_{i}^{\mathrm{ch}} \in [0,\overline{{p}}_{i}^{\mathrm{ch}}], \ \ {p}_{i}^{\mathrm{ds}} \in [0,\overline{{p}}_{i}^{\mathrm{ds}}],}
		\end{array}
		\hspace{-5pt} \right\} & \begin{matrix}
			\forall i \in \mc N^{\mathrm{st}}, \\ \forall h \in \mc H,
		\end{matrix} \\
		\edit{p_{i}^{\mathrm{ch}}= 0, \ \ p_{i}^{\mathrm{ds}}= 0,}\qquad \qquad & \forall i \notin \mc N^{\mathrm{st}},
	\end{aligned}
	\label{eq:x}
\end{equation}
where $x_{i,h} $ denotes the state of charge (SoC) of the storage unit at time $h \in \mc H$%
%\footnote{In \cite{atzeni2013}, the charging and discharging power are defined separately, which is actually a better representation. However, the optimal strategies that they produce satisfies the constraint that charging and discharging must be mutually exclusive (see footnote 1 in \cite{atzeni2013}). From other papers, they usually have boolean variables to ensure this constraint and we want to avoid that.}
, \edit{$\eta_i^{\mathrm{st}}, \eta_i^{\mathrm{ch}}, \eta_i^{\mathrm{ds}} \in (0,1]$ denote  the leakage coefficient of the storage, charging, and discharging efficiencies, respectively, while }  %$b_i~=~-\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}$, with 
$T_{\mathrm{s}}$ and $e^{\mathrm{cap}}_{i}$ denote sampling time and maximum capacity of the storage, respectively. Moreover, $\underline{x}_i,\overline{x}_i  \in [0,1]$  denote the minimum and the maximum SoC of the storage unit of prosumer $i$, respectively, whereas $\edit{\overline p}^{\mathrm{ch}}_i \geq 0$ and $\edit{\overline p}^{\mathrm{ds}}_i \geq 0$ denote the maximum charging and discharging power of the storage unit. Finally, we denote by  $\mathcal{N}^{\mathrm{st}}\subseteq\mathcal{N}$ 	the set of prosumers that own a storage unit.

@@

\item the local power unbalance $\eta_i$, defined as in \eqref{eq:etai} and privately communicated only to the DNO.

>>>>

%\paragraph*{highlight on considering physical constraints}
In practice, however, direct trading among prosumers might jeopardize system reliability, for which network operators are responsible. Therefore, when designing energy management mechanisms for a distribution grid, one must also consider the role of network operators and the reliability of the system itself.
%
For example, \cite{qin2018,morstyn2019} treat decentralized markets and operational reliability separately, and propose market-clearing mechanisms where decentralized market solutions must be approved by a network operator based on the system operational constraints. 
%
An alternative is based on incorporating network charges, which may reflect utilization fees and network congestion, into the market formulation, as discussed in \cite{baroche2019b,paudel2020}. Differently, \cite{moret2020,zhang2020} include network operators as players in the market and impose network operational requirements as constraints in the market problem, which is formulated as a multi-agent optimization. \marginnote{\note{R2-4}}\edit{A similar approach is considered in \cite{zhong2020cooperative}, which employs generalized Nash bargaining theory and decomposes the problem into two hierarchical subproblems (a social welfare maximization and an energy trading problem).}

\paragraph*{Contribution} 
In this paper, we consider a P2P energy market in which each prosumer is capable of not only generating and storing energy but also directly trading with other prosumers as well as with the main grid. Similarly to \cite{moret2020}, we include a network operator, whose objective is to ensure safe and reliable operation  of the system. 
%
However, we formulate the market clearing as a GNE problem, in which the players (i.e., prosumers and network operators) have coupling objective functions and constraints (Section \ref{sub:setup}). \marginnote{\note{R4-3}}\edit{Our market formulation extends the preliminary work \cite{belgioioso2020energy} by including network operational constraints and system operators in the model, which complicate the analysis as we need to exploit the problem structure to derive an efficient algorithm.}

@@

\smallskip
\subsubsection*{Notation}
$\R$ denotes the set of real numbers, $\bb N$ denotes the set of natural numbers, and  $\bs{0}$ ($\bs{1}$) denotes a matrix/vector with all elements equal to $0$ ($1$); to improve clarity, we may add the dimension of these matrices/vectors as subscript. $A \otimes B$ denotes the Kronecker product between the matrices $A$ and $B$. For a square matrix $A \in \R^{n \times n}$, its transpose is $A^\top$, $[A]_{i,j}$ represents the element on the row $i$ and column $j$. $A \succ 0$ ($\succcurlyeq 0$) stands for positive definite (semidefinite) matrix. Given $N$ vectors $x_1 \in \bb R^{n_1}, x_2 \in \bb R^{n_2},\ldots, x_N \in \R^{n_N}$, $x := \col\left(x_1,\ldots,x_N\right) = [ x_1^\top, \ldots , x_N^\top ]^\top$. \marginnote{\note{R4-9}}\edit{For any $x \in \bb R^n$, $\|x\|_A^2 = x^\top A x,$ with square matrix $A \succ 0$}. 
%\smallskip
%\subsubsection*{Operator theoretic definitions}
%Here, $\Id(\cdot)$ denotes the identity operator. The mapping $\iota_{S}:\R^n \rightarrow \{ 0, \, \infty \}$ denotes the indicator function for the set $\mc{S} \subseteq \R^n$, i.e., $\iota_{S}(x) = 0$ if $x \in S$, $\infty$ otherwise. 
For a closed set $S \subseteq \R^n$, the mapping $\proj_{S}:\R^n \rightarrow S$ denotes the projection onto $S$, i.e., $\proj_{S}(x) = \argmin_{y \in S} \left\| y - x\right\|$. 
%The set-valued mapping $\nc_{S}: \R^n \rightrightarrows \R^n$ denotes the normal cone operator for the the set $S \subseteq \R^n$, i.e., $\nc_{S}(x) = \varnothing$ if $x \notin S$, $\left\{ v \in \R^n \mid \sup_{z \in S} \, v^\top (z-x) \leq 0  \right\}$ otherwise. 
%A set-valued mapping $\mathcal{F} : \R^n \rightrightarrows \R^n$ is (strictly) monotone if $(u-v)^\top  (x-y) \geq (>) \, 0$ for all $x \neq y \in \R^n$, $u \in \mathcal{F} (x)$, $v \in \mathcal{F} (y)$.
% $\fix\left( \mathcal{F}\right) := \left\{ x \in \R^n \mid x \in \mathcal{F}(x) \right\}$ and $\zer\left( \mathcal{F}\right) := \left\{ x \in \R^n \mid 0 \in \mathcal{A}(x) \right\}$ denote the set of fixed points and of zeros, respectively.

@@

\begin{figure}
	\centering
	%\includegraphics[scale=1.4]{figures/37bus_ex}
	\includegraphics[width=\columnwidth]%
%{figures/NF/37bus_sysIPE1}%
{figures/37bus_sys_f1}
\smallskip
	\caption{Left plot: A modified IEEE 37-bus network with 12 prosumers (boxes) and 15 passive loads (black triangles); busses are represented by black circles, physical lines in $\mc L$ by solid lines. Right plot: P2P trading network, whereas trading relations ($\mc E$) are represented by blue double-arrow lines.
	}
	\label{fig:GGp}
\end{figure}

@@

\smallskip
\paragraph*{Storage units} 
Each prosumer might also minimize the usage of its storage units, for instance, in order to reduce its degradation. The corresponding cost function is denoted by $f_{i}^{\mathrm{st}}:\mathbb{R}^{H} \to \mathbb{R}$, defined as in \cite{hans2018}:
\begin{equation}
		%\marginnote{\note{R1-3}\\ \note{R2-2}}
f_{i}^{\mathrm{st}}(p_{i}^{\mathrm{ch}}, p_{i}^{\mathrm{ds}})= \|p_{i}^{\mathrm{ch}}\|_{Q_i^{\mathrm{st}}}^2 + \|p_{i}^{\mathrm{ds}}\|_{Q_i^{\mathrm{st}}}^2, \label{eq:f_st}
\end{equation}
where $Q_i^{\mathrm{st}}\succcurlyeq0$. \edit{The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics \cite{atzeni2013,zhong2019online}}
%
\begin{equation}
	\marginnote{\note{R1-3}\\ \note{R2-2}}
	\begin{aligned}
		\left.
		\begin{array}{c}
		\edit{	x_{i,h+1} =\eta_i^{\mathrm{st}} x_{i,h} +\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\frac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}),} \\[.2em]
			\underline{x}_i \leq x_{i,h+1} \leq \overline{x}_i, \\[.2em]
		\edit{	{p}_{i}^{\mathrm{ch}} \in [0,\overline{{p}}_{i}^{\mathrm{ch}}], \ \ {p}_{i}^{\mathrm{ds}} \in [0,\overline{{p}}_{i}^{\mathrm{ds}}],}
		\end{array}
		\hspace{-5pt} \right\} & \begin{matrix}
			\forall i \in \mc N^{\mathrm{st}}, \\ \forall h \in \mc H,
		\end{matrix} \\
		\edit{p_{i}^{\mathrm{ch}}= 0, \ \ p_{i}^{\mathrm{ds}}= 0,}\qquad \qquad & \forall i \notin \mc N^{\mathrm{st}},
	\end{aligned}
	\label{eq:x}
\end{equation}
where $x_{i,h} $ denotes the state of charge (SoC) of the storage unit at time $h \in \mc H$%
%\footnote{In \cite{atzeni2013}, the charging and discharging power are defined separately, which is actually a better representation. However, the optimal strategies that they produce satisfies the constraint that charging and discharging must be mutually exclusive (see footnote 1 in \cite{atzeni2013}). From other papers, they usually have boolean variables to ensure this constraint and we want to avoid that.}
, \edit{$\eta_i^{\mathrm{st}}, \eta_i^{\mathrm{ch}}, \eta_i^{\mathrm{ds}} \in (0,1]$ denote  the leakage coefficient of the storage, charging, and discharging efficiencies, respectively, while }  %$b_i~=~-\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}$, with 
$T_{\mathrm{s}}$ and $e^{\mathrm{cap}}_{i}$ denote sampling time and maximum capacity of the storage, respectively. Moreover, $\underline{x}_i,\overline{x}_i  \in [0,1]$  denote the minimum and the maximum SoC of the storage unit of prosumer $i$, respectively, whereas $\edit{\overline p^{\mathrm{ch}}_i} \geq 0$ and $\edit{\overline p^{\mathrm{ds}}_i} \geq 0$ denote the maximum charging and discharging power of the storage unit. Finally, we denote by  $\mathcal{N}^{\mathrm{st}}\subseteq\mathcal{N}$ 	the set of prosumers that own a storage unit.

@@

\item the active power injection $\eta_i$, defined as in \eqref{eq:etai} and privately communicated only to the DNO.
